Continous time Markov chain models; \\ extension, simulation and visualisation

### 2014-06-18 Chapter5.tex
todo list for ethods setion
minor changes

First computationally trackable models of codon substitution were independently proposed by \cite{Muse1994} and \cite{Goldman1994} and published in the same issue of Molecular Biology and Evolution (MBE).

@@

% computing the number of ways to 
% \begin{equation}
% TODO: Stirling number of the first class
% \label{eq:stirling} 
% \end{equation}

@@

>>>>

First computationally trackable models of codon substitution were independently proposed by \cite{Muse1994} and \cite{Goldman1994} and published in the same issue of Molecular Biology and Evolution (MBE).
For codon models the non-stop codon triplet $n_{1}n_{2}n_{3}$ is considered as a smallest unit of evoluton.
There are $4^3$ possible triplets minus three stop-codons, resulting in a state space size of $61$ codons.
The standard assuption of independence is used, i.e. the substitutions at these three codon positions occur independently, thus only a single change per triplet can occur at a given time.

% differences between models
% GY style models

@@

% computing the number of ways to 
% \begin{equation}
% TODO: Stirling number of the first kind
% \label{eq:stirling} 
% \end{equation}

@@

% Dirichlet distribution

% Dirichlet process
% - different constructions
